### 2020-10-11 input/background.tex
meow meow meow

\begin{definition}[Logical partition]
  A logical \underline{p}artition $P_s$ originated at a
  \underline{s}ource process $s \in V$ is a set of interconnected
  processes that do not belong to another logical partition.
\end{definition}

\begin{definition}[Optimal partitioning]
  The optimal partitioning $\mathcal{P}$ is a set of logical
  partitions such that each process belongs to a logical partition
  comprising its closest source process. $\forall p \in P_{s_1},
  \nexists P_{s_2}$ such that \TODO{$distance(p, s_2) < distance(p,
    s_1)$}.
\end{definition}

@@

@@

Algorithm~\ref{algo:add} shows the instructions of optimal
partitioning where the only operation available to processes is the
adding of partitions. Figure~\ref{fig:add} illustrates its behavior on
a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
$a$ and $c$ concurrently create a partition. They initialize their own
state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
receives $\alpha_{c}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. Process $b$
discards $\alpha_{b}^{1.5}$, for it does not improve its partition
distance. Processes $c$ and $d$ will never hear of Process $a$'s
partition. At scale, it saves bandwidth by limiting generated traffic
to subsets of processes. In Figure~\ref{fig:addD}, processes discard
last transiting messages. The system converged to the optimal
partitioning. Interestingly, while the receipt order of messages does
not impact on local control information, it impacts on control
information broadcast in the network.

>>>>

\begin{definition}[Logical partition]
  A logical \underline{p}artition $P_s$ originated at a
  \underline{s}ource process $s \in V$ is a set of interconnected
  processes that do not belong to another logical partition. The set
  of sources is $S$.
\end{definition}

\begin{definition}[Optimal partitioning]
  The optimal partitioning $\mathcal{P}$ is a set of logical
  partitions such that each process belongs to a logical partition
  comprising its closest source process. $\forall p \in P_{s_1\in S},
  \nexists P_{s_2 \in S}$ such that \TODO{$distance(p, s_2) <
    distance(p, s_1)$}.
\end{definition}

@@

\begin{definition}[Shortest path]
  A \underline{p}ath $\pi_{ij}$ from Process $i$ to Process $j$ is a
  sequence of vertices $[i, k_1, k_2, \ldots k_n, j]$ with $\forall
  0\leq m \leq n, \langle \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in
  E$. Shortest \underline{p}aths $\Pi_{ij}$ are sets of paths such
  that there exists no lower sum of weights from $i$ to $j$.
\end{definition}

\TODO{Define operation alpha. Receipt and deliveries.}

Without global knowledge, processes only rely on their own behavior to
deduce the behavior of their neighbor processes.

\begin{definition}[\label{def:pathdelivery}\TODO{Shortest path} delivery]
  \TODO{Shortest path} delivery ensures the system eventually converges to
  optimal partitioning:
  \begin{inparaenum}[(i)]
  \item (\textbf{termination}) processes do not need to propagate
    operations they do not deliver: $\forall \langle i, j \rangle \in
    E, \neg d_i(\alpha_{s}^w)\implies \neg
    d_j(\alpha_{s}^{w+w_{ij}})$;
  \item (\textbf{propagation}) operations delivered by a process may
    also benefit neighbor processes: $\forall \langle i, j \rangle \in
    E, d_i(\alpha_{s}^{w_1}) \implies
    d_j(\alpha_{s}^{w_1+w_{ij}}) \vee
    d_j(\alpha_{*}^{w_2 < w_1 + w_{ij}})$.
  \end{inparaenum}
\end{definition}

@@

Algorithm~\ref{algo:add} shows the instructions that implement the
rules of Definition~\ref{def:pathdelivery} to converge towards optimal
partitioning. Figure~\ref{fig:add} illustrates its behavior on a
system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
$a$ and $c$ concurrently create a partition. They initialize their own
state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
receives $\alpha_{c}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. Process $b$
discards $\alpha_{b}^{1.5}$, for it does not improve its partition
distance. Processes $c$ and $d$ will never hear of Process $a$'s
partition. At scale, it saves bandwidth by limiting generated traffic
to subsets of processes. In Figure~\ref{fig:addD}, processes discard
last transiting messages. The system converged to the optimal
partitioning. Interestingly, while the receipt order of messages does
not impact on local control information, it impacts on control
information broadcast in the network. \TODO{explain with r() d() b().}
